Hosted image editors often modify facial regions outside the anatomy named in a
cosmetic-surgery preview request, and every training-free localization method in
the literature needs model internals that a hosted endpoint does not expose. We
conduct a pilot benchmark of the control that remains available on the client:
six hosted editing configurations and one mask-specific inpainting endpoint on
facelift-style jaw--neck and rhinoplasty edits, under a three-rung ladder of
prompt only, a landmark-derived client-side masked composite, and
endpoint-native masked inpainting where available. Across \NumAttemptedEdits{}
attempted cells, \NumScoredEdits{} outputs were scoreable. ArcFace cosine
measures identity retention, while a CIELAB ratio measures change in the target
region relative to a predefined facial keep zone. Among the
\NumLocalizationFaces{} frontal faces for which regional scoring was available,
compositing increased localization over the paired prompt-only output by a
median of \MedPairedLocGain{} (95\% face-clustered bootstrap interval
\PairedLocGainLow--\PairedLocGainHigh) while retaining comparable on-target
pixel change. Model choice produced a visible edit-strength--identity
trade-off, and the single tested inpainting endpoint did not outperform
post-hoc compositing. The claims are scoped to control rather than clinical
accuracy: off-mask preservation holds by construction, no surgeon ratings were
collected, each cell contains one generated output, and postoperative
photographs serve only as identity references. Within that scope the result is
practical: region confinement for surgical previews requires no model access
and can be enforced uniformly, and cheaply, on the client.
