\section{Related Work}
\label{sec:related}

\textbf{Surgical outcome simulation.} Preoperative visualization predates
generative models by decades: manual computer morphing measurably improves
rhinoplasty patient satisfaction~\cite{sharp2002computerimaging}, its
expectation-management risks are equally well documented~\cite{agarwal2007morph},
and 3D simulation accuracy correlates with postoperative
satisfaction~\cite{yamamichi2025crisalix,threedvr2026aesthetic}. Learning-based
successors train bespoke models per procedure: a GAN trained on 3{,}030 paired
rhinoplasty photographs whose outputs raters could not distinguish from real
post-ops~\cite{knoedler2024rhinoplastygan}, appearance predictors for
blepharoptosis~\cite{blepharoptosis2022poap,huang2024ptosisdiffusion}, and
biomechanics-driven craniofacial simulation~\cite{fang2022acmtnet}; a recent
systematic review surveys the area~\cite{stephanian2024fpsamreview}. Closest to us,
Envisage~\cite{agarwal2026envisage} combines a local FLUX-based inpainter with
MediaPipe masks, hard compositing, and a mask-decomposed score built on masked
LPIPS~\cite{zhang2018lpips}. It evaluates rhinoplasty on 211 cases and shows why
full-face ArcFace scores are confounded after compositing. We address a narrower
systems question: six hosted black-box editing configurations rather than one
open-weight pipeline, two requested edit types, and control itself as the
manipulated variable. We do not reproduce Envisage's clinical presets,
mask-decomposed fidelity score, sample size, or ground-truth-relative analysis;
those differences limit direct quality comparisons. Lim et
al.~\cite{lim2023generativecosmetic} prompt text-to-image tools about the same
procedures but generate generic faces rather than editing a patient's photo.

\textbf{Training-free localized editing.} Methods that confine an edit without
fine-tuning uniformly reach inside a diffusion model~\cite{rombach2022ldm}:
SDEdit, RePaint, and DiffEdit steer the sampling
loop~\cite{meng2022sdedit,lugmayr2022repaint,couairon2023diffedit},
Blended (Latent) Diffusion blends masked latents at every denoising
step~\cite{avrahami2022blended,avrahami2023blendedlatent}, and Prompt-to-Prompt
and Plug-and-Play inject attention or
features~\cite{hertz2023prompt2prompt,tumanyan2023plugandplay}. A hosted endpoint
exposes none of those surfaces. Our masked composite is deliberately the
post-hoc remnant of this family, the final pixel-space blend applied after the
API returns, and the paper measures how far that remnant carries.

\textbf{Benchmarking instruction-guided editors.} General-domain benchmarks are
plentiful~\cite{brooks2023instructpix2pix,zhang2023magicbrush,wang2023editbench,
sheynin2024emuedit,ku2024imagenhub,ma2024i2ebench,hui2025hqedit,liu2025step1xedit},
and hosted commercial editors are now benchmarked
routinely~\cite{gptimgeval2025,qian2025giebench}. Off-target measurement also has
precedent: GIE-Bench scores object-masked preservation and finds that GPT-Image
over-edits irrelevant regions~\cite{qian2025giebench}, and ALE-Bench quantifies
attribute leakage outside the edit target~\cite{alebench2024}. These benchmarks
do not address cosmetic-surgery preview editing. Our pilot pairs an identity
diagnostic with facial target/keep-zone pixel change, but unlike clinically
validated outcome studies it has no surgeon ratings or input-relative
postoperative accuracy measure. ArcFace cosine itself is standard in face
editing~\cite{deng2019arcface}; neither it nor the CIELAB ratio is claimed as a
new or clinically validated metric.

\textbf{Face analysis.} The pipeline builds on MediaPipe's face
mesh~\cite{lugaresi2019mediapipe,grishchenko2020attentionmesh} with InsightFace's
SCRFD detection and landmarks as the profile fallback~\cite{guo2022scrfd}, and on
CIELAB color difference~\cite{sharma2005ciede2000} for the regional metric.
