\section{Method}
\label{sec:method}

We treat each editing model as a black box behind a hosted endpoint: it accepts an
image and a text instruction and returns an edited image. No weights, latents,
attention maps, or sampling loop are exposed, so the training-free localization
methods surveyed in Sec.~\ref{sec:related} do not apply. Everything we add runs on
the client, before the request or after the response.

\subsection{The control ladder}
\label{sec:ladder}

A procedure specification consists of a target region $r$ (jaw and neck for the
facelift-style request, nose for rhinoplasty), a positive instruction describing
the visible anatomical change, and a list of changes to avoid. We compare three
rungs of increasing client-side control, holding faces, model settings, and
prompts fixed. A common seed is supplied to every endpoint; the GPT Image~2 and
Seedream~5.0 Lite schemas have no seed field and ignore it:

\begin{itemize}
  \item \textbf{Prompt only.} The photo and instruction go to the endpoint
  unmodified and the response is used as-is. This measures what the model does when
  instructed to edit one region.
  \item \textbf{Masked composite.} The endpoint still edits the whole image, but we
  discard everything outside $r$: the response is aligned back onto the input and
  composited through a feathered region mask (Sec.~\ref{sec:composite}), so pixels
  outside the mask remain identical to the input by construction.
  \item \textbf{Masked inpaint.} For endpoints that accept an explicit mask, we send
  the region mask with the request and let the model inpaint inside it.
\end{itemize}

The ladder is the experimental variable, not a new editing algorithm: pixel-space
blending is the final step of Blended Diffusion~\cite{avrahami2022blended} and of
Envisage's hard composite~\cite{agarwal2026envisage}. What we study is how much of
the localized-editing problem this post-hoc adaptation solves when nothing inside
the model can be touched.

\subsection{Landmarks and region masks}
\label{sec:masks}

Region masks derive from MediaPipe's 478-point face
mesh~\cite{lugaresi2019mediapipe,grishchenko2020attentionmesh}. Each region is the
convex hull of a landmark subset: the face splits at the lower-eyelid line into an
upper-face zone (forehead, brows, and eyes, which a facelift must not change) and a
jaw--neck zone (cheeks, nasolabial folds, jowls, jawline, chin). The mesh has no
neck landmarks, so the jaw--neck hull extends below the chin by a fixed fraction of
face height. The nose region is a perimeter hull dilated by a margin proportional
to the inter-ocular distance, which also scales every feather and erosion radius so
the masks are resolution-independent.

MediaPipe finds no face on true profile views. For the nose region we fall back to
InsightFace's SCRFD detector with its 106-point landmark
set~\cite{guo2022scrfd}, scaled by the detection box; the remaining regions are
defined only by the frontal mesh and are pose-gated instead (below).

\subsection{Masked compositing and pose gating}
\label{sec:composite}

Hosted editors routinely shift, rescale, or re-crop the head, so pasting the raw
response through a mask produces double contours. We first align the edited image
onto the input with a similarity warp estimated from stable landmark anchors, then
blend: $\mathrm{out} = x\,(1-w) + e\,w$, where $x$ is the input, $e$ the aligned
edit, and $w$ a per-pixel weight from the feathered mask.

The composite mask is shaped so its boundary never crosses visually busy texture.
Relative to the metric region it is eroded off the face silhouette, clipped medial
of the ears so the seam avoids the sideburns, extended further down the neck so a
narrowed jawline blends into shadow or clothing, and feathered with a wide
smoothstep ramp over the signed distance to the mask boundary rather than a
Gaussian blur. All widths are inter-ocular fractions.

Compositing is skipped when the estimated yaw exceeds $0.35$. In early profile
rhinoplasty runs the frontal-only hulls landed on the wrong part of the face and
pasted a translucent ``ghost nose'' onto the cheek; gating on pose returns the
unmodified edit for those inputs rather than a corrupted one.

\subsection{Prompt guardrails}
\label{sec:guardrails}

The dominant failure mode we observed is not refusal but \emph{generic
beautification}: smoothed skin, brightened teeth, and subtly enlarged eyes. Every
request therefore carries three fixed instruction fragments in addition to the
procedure text. An avoidance fragment lists the beautification behaviors
(``beauty filter, skin smoothing,
airbrushing, wrinkle removal, \ldots{} different person, identity change, face
swap''), a positive fragment anchors realism and framing (``photorealistic, same
person, identity preserved, natural skin texture, identical camera framing''), and
an intensity fragment scopes the change to anatomy (``change only facial tissue and
contour; keep skin tone, color, exposure, and lighting identical to the input'').
Where a separate negative-prompt field exists, the avoidance fragment is supplied
there; otherwise it is appended to the main instruction. The prompts request a
visible anatomical correction because target and off-target changes are reported
together (Sec.~\ref{sec:protocol}).
