\section{Evaluation Protocol}
\label{sec:protocol}

An edit can change too much outside the requested region or too little inside it.
Our automated protocol records both directions, but it is a systems diagnostic:
it does not establish whether an edit is anatomically or clinically plausible.

\subsection{Identity}

We compute the cosine similarity between ArcFace~\cite{deng2019arcface}
embeddings of the largest detected face in the input and in the edit. We plot
$0.6$ as a heuristic reference threshold, not a clinically calibrated acceptance
criterion; verification thresholds depend on implementation, preprocessing, and
the desired false-match rate. A high score can also mean the model did not perform
the edit, so identity is read with the regional-change scores below.

As Agarwal and Bhrany~\cite{agarwal2026envisage} note, a full-face identity score
on a composited output is partly determined by pixels copied from the input. We
therefore treat prompt-only identity as a model-level diagnostic and composite
identity as a system-level property. Neither score measures surgical accuracy.

\subsection{Regional change and localization}

After aligning the edit onto the input, we convert both to CIELAB and take the
mean $\Delta E_{76}$ color difference inside the requested target region
($\Delta E_{\mathrm{tgt}}$) and inside a disjoint facial keep zone
($\Delta E_{\mathrm{off}}$, the upper-face region minus the target). We use the
simple 1976 distance rather than the perceptually refined
CIEDE2000~\cite{sharma2005ciede2000}; it is a reproducible pixel-change
diagnostic, not a perceptual or anatomical accuracy score. The summary statistic
is
\[
  \mathrm{loc} = \frac{\Delta E_{\mathrm{tgt}}}
                      {\Delta E_{\mathrm{tgt}} + \Delta E_{\mathrm{off}}}.
\]
The ratio is read with its components: low $\Delta E_{\mathrm{tgt}}$ identifies
a near-copy, while high $\Delta E_{\mathrm{off}}$ indicates leakage into the
measured keep zone. Related preservation metrics appear in general-domain editing
benchmarks~\cite{qian2025giebench,alebench2024,sheynin2024emuedit}.

Three limitations are important. First, the keep zone does not cover the entire
image; lower-face, hair, clothing, or background changes may be missed,
particularly for rhinoplasty. Second, the frontal-mesh metric abstains on profile
inputs. Third, compositing copies off-mask pixels by design, so a high ratio on
that rung verifies the implementation's preservation property rather than the
editor's quality.

\subsection{Postoperative identity reference}

For faces with a postoperative photograph, we report the ArcFace cosine between
the edit and that photograph. This is an identity-continuity reference only. The
sessions differ in pose, expression, makeup, and hair, and the present run records
do not include the input-to-postoperative baseline needed to test whether an edit
moved closer to the observed outcome. We make no outcome-accuracy claim from this
score.

\subsection{Descriptive uncertainty}

The face, not the generated edit, is the sampling unit. Cell summaries remain
medians and ranges because each model--control cell contains fewer than ten faces.
For the primary prompt-only versus masked-composite contrast, we compute paired
differences within face, procedure, and model, then resample faces (10{,}000
replicates, fixed analysis seed) to obtain a percentile interval for the median.
This interval describes the observed face set; it does not repair the small sample
or support population-level clinical inference.

\subsection{Expert rubric (future protocol)}

We release a proposed seven-axis rubric: identity preservation, photorealism,
procedure specificity, clinical plausibility, edit localization, consistency,
and safety of the expectation set. Each axis is scored 1--5, with clinical
plausibility reserved for a surgeon. Suggested pass thresholds have not been
clinically calibrated. No rubric scores were collected here; a blinded,
multi-surgeon study with inter-rater agreement is required before clinical claims
(Sec.~\ref{sec:conclusion}).
