\section{Experimental Setup}
\label{sec:setup}

\begin{table}[t]
  \centering
  \caption{Endpoints in the study. All run behind fal.ai; cost is the provider's
  estimate on July 16, 2026. Aliases may change after that date.}
  \label{tab:models}
  \resizebox{\columnwidth}{!}{\input{tables/setup_models}}
\end{table}

\textbf{Models.} Table~\ref{tab:models} lists six hosted editing configurations:
OpenAI GPT Image~2 at two quality tiers~\cite{openai2026gptimage2}, Google's Nano
Banana~Pro and Nano Banana~2~\cite{google2025nanobananapro,google2026nanobanana2},
ByteDance Seedream~5.0 Lite~\cite{seedream5lite_2026,seedream4_2025}, and
FLUX.2~[pro]~\cite{bfl2025flux2,bfl2025fluxkontext}. A Qwen-Image-Edit endpoint
provides the masked-inpaint rung~\cite{wu2025qwenimage}. Hosted services are moving
targets, so every run records its date and endpoint alias. The provider did not
expose immutable revisions for every model.

\textbf{Data.} The full pool contains real, publicly accessible before/after
photograph pairs: 12 frontal facelift inputs (11 with a paired postoperative
photograph) and 14 rhinoplasty inputs (10 profile views and 4 frontal cross-views,
all paired). The benchmark matrix uses 8 facelift faces and 8 rhinoplasty faces
(the 4 frontal cross-views, which the regional metric can score, plus 4 profiles
that contribute identity and postoperative-reference evidence). Faces are drawn
independently per requested edit type; no person appears in both sets. One
extreme-profile rhinoplasty face defeats the identity detector on every edit
(Sec.~\ref{sec:failures}), so the main analysis contains \NumPrimaryFaces{}
faces. With the separate chained-experiment face included, \NumFacesScored{}
distinct faces contribute scoreable outputs, and the rhinoplasty rows of
Table~\ref{tab:main} hold 7 rather than 8 faces.

Images are normalized to $1024^2$ with padding. These are identifiable,
health-related photographs even when publicly viewable. The exact source terms,
republication permission, and institutional-review determination must be
documented before archival submission (Sec.~\ref{sec:ethics}). No private
clinical records were used.

\textbf{Protocol.} Runs expand a Cartesian matrix of faces $\times$ models
$\times$ requested edit types $\times$ controls. A common seed is passed to
every endpoint; the GPT Image~2 and Seedream~5.0 Lite schemas have no seed field
and ignore it. One output is generated per cell, so the study does not estimate
within-endpoint stochastic variation. The gallery renderer shows attempted cells,
and provider or scoring failures remain in the run records. Each immutable run
directory stores its resolved configuration and git commit; output filenames
encode the full cell key used for scoring. Generation and scoring are decoupled,
so metrics can be recomputed without new API requests.

The reported results come from a designated set of matrix runs executed after the
pipeline was frozen; earlier development runs are retained but not pooled. One
additional experiment applies rhinoplasty and facelift-style edits to the same
face in both orders as a feasibility check. The full design attempted
\NumAttemptedEdits{} outputs: \NumScoredEdits{} were scoreable and
\NumExcludedEdits{} were unavailable because one inpainting request was rejected
and one extreme-profile face failed identity detection across 13 cells. Across
scoreable outputs, median latency is \MedLatency{}\,s and median provider cost is
\$\MedCost{} per image.

The paper's numeric values are generated by an aggregation script from the run
records. Duplicate stems are resolved by keeping the row with the most complete
metric set. The public repository includes the canonical score table and analysis
scripts, but not the source photographs or full generation pipeline; it therefore
supports audit of reported summaries rather than end-to-end reproduction.
