\section{Ethics and Privacy}
\label{sec:ethics}

\textbf{Identifiable images.} The study uses publicly accessible before/after
photographs rather than private clinical records. Public access, however, does not
by itself establish consent for research, republication, or transmission to hosted
AI services. Before archival submission, the authors must record each source and
its terms, confirm figure-republication and hosted-processing rights, provide any
required attribution, and obtain an institutional IRB or exemption determination.
The current paper should not be read as documenting those approvals.

\textbf{Accounting.} The design attempted every cell in the specified matrix.
Table~\ref{tab:main} contains every scoreable output, while one rejected request
and 13 detector failures are reported explicitly rather than silently omitted.
Qualitative figures are selected for legibility and are not evidence of prevalence;
the canonical score table supports quantitative auditing.

\textbf{Intended use and misuse.} A preview is an expectation-setting aid, not a
promised outcome. Over-idealized previews can create expectations that surgery
cannot meet~\cite{agarwal2007morph}. The present system has not been clinically
validated and should not guide treatment or be shown as a predicted outcome. The
same editing capability applied to a non-consenting person's photograph is
harmful. Any deployment should verify subject authorization, disclose synthetic
content and uncertainty, retain the original image, and log the endpoint and
settings. Model-card documentation practices~\cite{mitchell2019modelcards} apply
to systems assembled from hosted APIs as well as to their component models.

\textbf{Fairness.} The demographic makeup of the test set is unrecorded, and face
analysis systems can exhibit demographic performance gaps
~\cite{buolamwini2018gendershades}. A stratified evaluation and failure analysis
are prerequisites for any clinical-use claim.
